### 2013-10-19 paper/paper.tex
Added preamble and content to paper.tex

\section{Introduction}

@@

McCabe etc

@@

>>>>

\documentclass[11pt,twoside,a4paper]{article}
\usepackage{amssymb, amsmath}

\begin{document}
\section{Introduction}

@@

\begin{enumerate}
\item[Source Line of Code] To define SLOC we use the definition given by Conte [Conte 1986]:
A line of code is any line of program text that is not a comment or blank line, regardless of the
number of statements or fragments of statements on the line. This specifically includes all lines containing program headers, declarations, and executable and non-executable statements.

\item[Lines of Code (LOC)]  Lines of code refers to the total number of lines in each source code file including comments and blank lines. It is a straightforward measure and can be calculated using many available tools.

\item[McCabe's Cyclomatic Complexity]
McCabe’s Cyclomatic complexity is one of the earliest complexity measures developed by Thomas J. McCabe in 1976. It directly measures the number of linearly independent paths through a program's source code. Any program can be represented as a graph with the simplest element being a flat series of statements with no conditions, loops or branches. [1] For a graph $G$ with $n$ vertices, $e$ edges and $p$ exit points, the complexity $v$ is defined as follows:

\begin{equation}
v(G)=e-n+2p
\end{equation}

It is worth mentioning that the minimum value for the cyclomatic complexity metric is 1, which corresponds to the flat series of statements with no bifurcations or loops. Every additional region in the flow graph would increase the Cyclomatic complexity by one unit.

@@

\end{document}
